---
title: "bbsBuildArtifacts: comparing BBS states over time"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{bbsBuildArtifacts: comparing BBS states over time}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

# Identifying packages with new events relative to a prior build

We have created "trimmed tarballs" from two dates: Dec 10 2021
and Jan 5 2022 and included these with the package.

Here's the more recent one.
```{r lktwo}
 suppressPackageStartupMessages({
  library(bbsBuildArtifacts)
 })
 af2 = make_demo_ArtifSet(url = demo_url2(),
        demostring = "test_report_3.14_bioc_20220105", destbase = "test_report_0105")
 af2
```

The default demonstration ArtifSet is from Dec 10 2021.
```{r lk1}
 af1 = make_demo_ArtifSet()
 af1
```

The `new_events` function will enumerate packages exhibiting new events.
Arguments to the function specify the build phase and event
type to be sought.
```{r lkne}
 new_events(af1, af2)
```
This report is host-dependent; the default here was nebbiolo2.
```{r lkne2}
 new_events(af1, af2, host="tokay2")
```

# Packages for which events have resolved

```{r lkres}
 becomes_OK(af1, af2)
 becomes_OK(af1, af2, host="tokay2")
```

# Comprehensive comparison

```{r lkcomp}
hn = slot(af1, "hostnames")
lapply(hn, function(x) becomes_OK(af1, af2, host=x))
```

Also iterate over event types.  Note that resolution of events to OK does not
imply that the identified packages have been changed.  The dependency
graph could be used to find the causative package.

We have recently added `available_artifs()` to provide information
on dates and versions of artifact sets in cache.
