---
title: "Scanning a series of build reports"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Scanning a series of build reports}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

# Introduction


Build reports on 3.17 were collected from 2023-06-15 to 2023-07-15.

The report.tgz are cached using a cron job that in turn uses R and
bbsBuildArtifacts.  This takes care of locating and renaming the
report.tgz files.

```
# m h  dom mon dow   command
37 12 * * * Rscript -e 'library(bbsBuildArtifacts); setup_artifacts(version="3.17", hostnames=c(linux="nebbiolo1", macos="merida1"))' >> mylog.log
37 13 * * * Rscript -e 'library(bbsBuildArtifacts); setup_artifacts(version="3.18", hostnames=c(linux="nebbiolo2", macos="lconway"))' >> mylog.log
```

The entries of the log file look like:
```
bsBuildArtifacts ArtifSet instance.
  2230 pkg paths for type bioc, Bioconductor version 3.17.
  23 extra file paths.
  tarball production date: 2023-07-14
R version: 4.3.1 (2023-06-16) -- "Beagle Scouts"
Platforms:
  Linux (Ubuntu 22.04.2 LTS)
  macOS 12.6.4 Monterey
Use paths(aset)[...] to retrieve selected paths.
bbsBuildArtifacts ArtifSet instance.
  2214 pkg paths for type bioc, Bioconductor version 3.18.
  26 extra file paths.
  tarball production date: 2023-07-15
R version: 4.3.1 (2023-06-16) -- "Beagle Scouts"
Platforms:
  Linux (Ubuntu 22.04.2 LTS)
  macOS 12.6.5 Monterey
Use paths(aset)[...] to retrieve selected paths.
```

There are version-, host-, package-, and phase-specific data collected
on all software packages every time `setup_artifacts` is run.  Our task
is to harvest the information in ways that are useful to developers and core.

# Time series extraction

We serialized the results of `scan_artifs` for dates ranging
from 2023-06-15 to 2023-07-15.  This was done for 3.17 and 3.18.
Two types of information are retrieved in these scans -- the
number of OK outcomes for installation, and the number of OK outcomes
for checksrc.

```{r setup,message=FALSE}
library(bbsBuildArtifacts)
data(scan_demo_3.17)
scan_demo_3.17
```

We visualize the series:

```{r lks}
plot_scan_inst(scan_demo_3.17) + ggplot2::ylim(2120,2250)
```

Similarly for checksrc outcomes:

```{r lks2}
plot_scan_chk(scan_demo_3.17) + ggplot2::ylim(1590,1720)
```
